Time slice analyses

### 2017-12-15 analyses/02-time-slice-analyses.Rmd
Corrected incorrect root age for Wright

## Loading the tree
## See "01-extract-data-for analyses.Rmd" for how we cleaned these
tree <- read.nexus(paste0("../data/processed/tree.", slug, ".tre"))
## Add root age as defined in Wright 2017
tree$root.time <- 484.4

>>>>

## Loading the tree
## See "01-extract-data-for analyses.Rmd" for how we cleaned these
tree <- read.nexus(paste0("../data/processed/tree.", slug, ".tre"))
## Add root age as defined in Wright 2017
tree$root.time <- 485.4
